Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-04-27 ProbabilisticCoherence.tex
Reorganisation of section 5.2.2 and some open questions posed

@@

Any coherent hierarchical forecast density is a degenerate density. To the best of our knowledge, there is no proper multivariate scoring rule available to evaluate degenerate densities. Further, it can easily be seen that some of the existing scoring rules breakdown under degeneracy.

However, even though the coherent distribution of the entire hierarchy is degenerate, the density of the basis set of series is non-degenerate since these series are linearly independent. Further, if we can correctly specify the forecast distribution of the basis set of series, then we have almost obtained the correct forecast distribution of the whole hierarchy. Therefore, we propose to evaluate the forecast distributions using only the basis set of series. Then we can use any of the multivariate scoring rules discussed above without incurring problems due to degeneracy.

For example, since the bottom-level series forms a set of basis series for a given hierarchy, we can evaluate the coherent forecast distribution using only the bottom-level series instead of evaluating the whole distribution. In particular, if our purpose is to compare two coherent forecast densities, we can compare them using only the bottom-level forecast densities.

>>>>

\todo{Stuff below still open}

@@

A characteristic of coherent probabilistic forecasts is that they can be completely characterised in terms of basis series. If probabilistic forecasts of the basis series are accurate, then forecasts for the whole hierarchy are also accurate. Therefore, we propose that two different sets of reconciled forecasts can be compared to one another using only the basis set of series. Then we can use any of the multivariate scoring rules discussed above without incurring problems due to degeneracy.  For example, since the bottom-level series forms a set of basis series for a given hierarchy, we can evaluate the coherent forecast distribution using only the bottom-level series instead of evaluating the whole distribution. 
\todo{Two questions below}

\begin{itemize}
	\item Can we prove that if reconciled forecast A is better than forecast B in terms of the bottom level then it will also be better for the whole series.  This is kind of obvious for log score, but may not be for energy score and variogram score
	\item Does the basis we use matter.  We know that energy score is invariant to orthogonal rotations but ${\bm S}$ is not (semi) orthogonal.  On the other hand, I don't think variogram is invariant to rotations as all unless $p=2$.
\end{itemize}
